---
title: "Introduction to gridstackeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_gridestakeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Getting started

In the ```ui.R``` file, create a grid using ```grid_stack(...)``` and place grid-stack-items inside using ```grid_stack_item(...)```.

Specify options like height, width, x-, y-position as well. Check the [gridstack.js documentation](https://github.com/gridstack/gridstack.js/tree/master/doc#item-options) for a full list of options.

The ```ui.R``` file might contain something like the following.
```{r, eval=FALSE}
grid_stack(
  grid_stack_item(
    h = 4, w = 4, id = "plot_container", style = "overflow:hidden",
    shinydashboard::box(
      title = "Histogram", status = "primary", solidHeader = TRUE,  width = 12, height = "100%",
      plotOutput("plot", height = "auto")
    )
  )
)
```

## Dynamic figure height

Elements inside ```grid-stack-item``` might not change their height automatically. See the following code examples to make sure all your elements correctly resize.

### Setting the height dynamically using callbacks
The following example shows how the height of the plot can be set dynamically using the ```<id>_height``` callback

Note: the ```plot_container_height``` references the height of the ```id = "plot_container"``` created in the ```ui.R``` example above.


```{r, eval=FALSE}
output$plot <- renderPlot({
    x    <- faithful$waiting
    bins <- seq(min(x), max(x), length.out = input$slider + 1)

    hist(
      x, breaks = bins, col = "#75AADB", border = "white", 
      xlab = "Waiting time to next eruption (in mins)", 
      main = "Histogram of waiting times"
    )
  },
  # set the height according to the container height (minus the margins)
  height = function() {
    min_height <- 150
    margin <- 80
    max(input$plot_container_height - margin, min_height)
  }
)
```



### Setting the height for [DT::dataTableOutput](https://rstudio.github.io/DT/)
The height for a ```DT::dataTableOutput``` can be set as in the following example.

ui.R
``` {r, eval=FALSE}
grid_stack_item(
        w = 4, h = 10, x = 0, y = 0, id =  "c_table",
        DT::dataTableOutput("mytable")
      )
``` 

server.R
``` {r, eval=FALSE}
output$mytable <- DT::renderDataTable({
    DT::datatable(mtcars, options = list(
      # set the height according to the container height (minus the margins)
      scrollY = max(input$c_table_height, 200) - 110, paging = FALSE
      )
    )
  })
```

### Setting the height for [echarts4r](https://github.com/JohnCoene/echarts4r)
The height for a ```echarts4r::echarts4rOutput``` can easily be set using the ```height="100%"``` option.

ui.R
``` {r, eval=FALSE} 
grid_stack_item(
 w = 5, h = 5, x = 7, y = 0, id = "c_plot",
 echarts4rOutput(outputId =  "plot", height = "100%")
)
``` 


## Installation

```r
# latest devel version
devtools::install_github("petergandenberger/gridstackeR")
```

## Demo

See a working example on shinyapps.io [here](https://pega.shinyapps.io/gridstackeR).

